Under-ice acoustic navigation using real-time model-aided range estimation

### 2022-02-19 manuscript/main.tex
finalized figs

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figs/trilat-stat.pdf}
\caption{WRITE THIS.}
\label{fig:trilat}
\end{figure}

@@

FIG A -- error for MBC/NBC (Oscar Fig 6.17). Think about whether to include separate in situ column. Explain why this section uses error whereas previous section uses correction.

I think if we go down this route, we can take out the GNSS noise section entirely. The POMA paper would go over GNSS noise at high latitudes, crossmap, and look at individual drifts. I do not think the crossmap needs to stay in this publication; given small numerical value of the re-positioning trilateration, I think the same point is made (in a better way, actually).

>>>>

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figs/beacon-trilat-stat.pdf}
\caption{WRITE THIS.}
\label{fig:trilat-beacon}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figs/auv-trilat-stat.pdf}
\caption{WRITE THIS.}
\label{fig:trilat-auv}
\end{figure}
